Temporal Developer Concept Witchery: Latent Dirichlet Allocation Applied to Revisions

### 2009-02-18 presentation/presentation.out.tex
Renamed
more presentation changes

\documentclass[titlepage,usenames,a4,landscape,semhelv,16pt]{seminar}
\newcommand{\presenter}{Abram Hindle}
\newcommand{\conference}{}
\newcommand{\gettitle}{Temporal Developer Concept Witchery: Latent Dirichlet Allocation Applied to Revisions}

@@

\newslide
\igbigcapb{commit-to-topics}{How commits are aggregated into Topics}

@@

@@

		\end{itemize}
	\end{itemize}
\end{itemize}
\end{itemize}
\sslide{LDA}
\begin{itemize}
\item Latent Dirichlet Allocation
\item Like Latent Semantic Indexing (LSI)
\item Like ICA/PCA
\item Black box view:
	\begin{itemize}
	\item Input word distributions of messages, 
	\item Output topics consisting of a word distribution and related messages

@@

%\igninetycap{transitiveclosure}{Clustering topics (black dots) by Transitive Closure based on similarity (arcs)}
\igonecap{transitiveclosure}{Clustering topics (black dots) by Transitive Closure based on similarity (arcs)}

\end{itemize}
\end{itemize}
\sslide{Case Study: Portability}
\begin{itemize}
\item MySQL 3.23 
	\begin{itemize}
	\item Discussions relating to portability
	\item Some topics smeared across multiple months

@@

@@

%\igbigslidecap{lda}{Example of topics extracted from MySQL 3.23}
%\igonecap{lda}{Example of topics extracted from MySQL 3.23}
%\igbigcapb{lda}{Example of topics extracted from MySQL 3.23}
%\igbigthirtycapb{lda}{Example of topics extracted from MySQL 3.23}
\igbigthirtyfivecapb{lda}{Example of topics extracted from MySQL 3.23}

@@

	\end{itemize}
\end{itemize}
\end{itemize}
\sslide{Unfinished}
\begin{itemize}
\item Total Topics versus Monthly Topics

\end{itemize}
\sslide{Future work}
\begin{itemize}
\item Extension, associate Trends or Topics with purpoes by using wordnet and Taxonomies of software quality

\end{itemize}
\end{slide}

>>>>

\documentclass[titlepage,usenames,a4,landscape,semhelv]{seminar}
\newcommand{\presenter}{Abram Hindle}
\newcommand{\conference}{}
\newcommand{\gettitle}{Temporal Developer Concept Witchery: Latent Dirichlet Allocation Applied to Revisions}

@@

@@

\end{itemize}
\end{itemize}
\sslide{LDA}
\begin{itemize}
\item Latent Dirichlet Allocation
\item Like Latent Semantic Indexing (LSI)
\item Like ICA/PCA
\item Black box view:
	\begin{itemize}
	\item Input word distributions of messages, 
	\item Output topics consisting of a word distribution and related messages

%\newslide

\igonecap{transitiveclosure}{Clustering topics (black dots) by Transitive Closure based on similarity (arcs)}

@@

@@

%\igninetycap{transitiveclosure}{Clustering topics (black dots) by Transitive Closure based on similarity (arcs)}

%\igbigcapb{commit-to-topics}{How commits are aggregated into Topics}
\begin{specquotei}
\begin{center}
\noindent
\includegraphics[width=1.25\textwidth]{commit-to-topics} \\
{How commits are aggregated into Topics}
\end{center}
\end{specquotei}

		\end{itemize}
	\end{itemize}
\end{itemize}
\end{itemize}
\sslide{Case Study: Portability}
\begin{itemize}
\item MySQL 3.23 
	\begin{itemize}
	\item Discussions relating to portability
	\item Some topics trends (topics smeared across multiple months)

@@

%\igbigslidecap{lda}{Example of topics extracted from MySQL 3.23}
%\igonecap{lda}{Example of topics extracted from MySQL 3.23}
%\igbigcapb{lda}{Example of topics extracted from MySQL 3.23}
%\igbigthirtycapb{lda}{Example of topics extracted from MySQL 3.23}

%\newslide

\igbigthirtyfivecapb{lda}{Example of topics extracted from MySQL 3.23. This is the kind of plot we eventually want to produce: named topics and topic trends}

%\newslide

\end{itemize}
\end{itemize}
\sslide{Case Study: MaxDB 7.500}
\begin{itemize}
\item Autogenerated plots from MaxDB 7.500
\item Multiple Presentations
	\begin{itemize}
	\item Condensed view
	\item Trend Histogram 
	\item Trend View
	\item Trend Timeline

\igbigcap{fixed-time-smear-plot-cropped}{Slice of Topics per Month for MaxDB 7.500}

%\newslide

\igonecap{fixed-time-smear-plot-scaled}{Entire View of Topics per Month for MaxDB 7.500}

%\newslide

%\igninetycap{histogram-cropped}{}

%\newslide

\igHeigthyfivecap{histogram-cropped-scaled}{Top part of trend histogram, ordered by topic occurance}

@@

\igonecap{class-smear-plot-crop-scaled}{Trend Time Line: Trends plotted over time of MaxDB 7.500}

%\igbigcapb{class-smear-plot-crop-scaled-zoomed}{Zoomed in view of the repeating topics plotted}
\begin{specquoteh}
\begin{center}
\includegraphics[width=1.25\textwidth]{class-smear-plot-crop-scaled-zoomed} \\
Zoomed in view of the trend time line
\end{center}
\end{specquoteh}

%\igbigcapb{class-smear-plot-crop-scaled-zoomed}{Zoomed in view of the repeating topics plotted}

@@

	\end{itemize}
\end{itemize}
\end{itemize}
\sslide{Unfinished}
\begin{itemize}
\item Total Topics versus Monthly Topics
\item Clean up plots

\end{itemize}
\sslide{Future work}
\begin{itemize}
\item Cluster Naming
\item Associate trends with software taxonomies
	\begin{itemize}
	\item Extension, associate Trends or Topics with purpoes by using wordnet and Taxonomies of software quality as suggested by Ernst et al.
\end{itemize}
\item Validation

\end{itemize}
\sslide{Conclusions}
\begin{itemize}
\item Contributions
	\begin{itemize}
	\item Auto extract trends
		\begin{itemize}
		\item Present trends
\end{itemize}
	\item Apply topic analysis on timewindows rather than the entire project

\end{itemize}
\end{itemize}
\end{slide}

### 2009-02-18 presentation/presentation.tex
more presentation changes

@@

@@

%\igninetycap{transitiveclosure}{Clustering topics (black dots) by Transitive Closure based on similarity (arcs)}
\igonecap{transitiveclosure}{Clustering topics (black dots) by Transitive Closure based on similarity (arcs)}

@@

@@

%\igbigslidecap{lda}{Example of topics extracted from MySQL 3.23}
%\igonecap{lda}{Example of topics extracted from MySQL 3.23}
%\igbigcapb{lda}{Example of topics extracted from MySQL 3.23}
%\igbigthirtycapb{lda}{Example of topics extracted from MySQL 3.23}
\igbigthirtyfivecapb{lda}{Example of topics extracted from MySQL 3.23}

>>>>

=Developer Trends
* Trends
** Continuous or repeating topics
** Occur over multiple time windows

=LDA
* Latent Dirichlet Allocation
* Like Latent Semantic Indexing (LSI)
* Like ICA/PCA
* Black box view:
** Input word distributions of messages, 
** Output topics consisting of a word distribution and related messages

@@

%\newslide

\igonecap{transitiveclosure}{Clustering topics (black dots) by Transitive Closure based on similarity (arcs)}

=Topic Similarity
* Given 2 topics
** if their top 10 words 
*** share X words (7 or more)
****  they are similar

@@

%\igninetycap{transitiveclosure}{Clustering topics (black dots) by Transitive Closure based on similarity (arcs)}

%\igbigcapb{commit-to-topics}{How commits are aggregated into Topics}
\begin{specquotei}
\begin{center}
\noindent
\includegraphics[width=1.25\textwidth]{commit-to-topics} \\
{How commits are aggregated into Topics}
\end{center}
\end{specquotei}

=Case Study: Portability
* MySQL 3.23 
** Discussions relating to portability
** Some topics trends (topics smeared across multiple months)

@@

%\igbigslidecap{lda}{Example of topics extracted from MySQL 3.23}
%\igonecap{lda}{Example of topics extracted from MySQL 3.23}
%\igbigcapb{lda}{Example of topics extracted from MySQL 3.23}
%\igbigthirtycapb{lda}{Example of topics extracted from MySQL 3.23}

%\newslide

\igbigthirtyfivecapb{lda}{Example of topics extracted from MySQL 3.23. This is the kind of plot we eventually want to produce: named topics and topic trends}

%\newslide

=Case Study: MaxDB 7.500
* Autogenerated plots from MaxDB 7.500
* Multiple Presentations
** Condensed view
** Trend Histogram 
** Trend View
** Trend Timeline

\igbigcap{fixed-time-smear-plot-cropped}{Slice of Topics per Month for MaxDB 7.500}

%\newslide

\igonecap{fixed-time-smear-plot-scaled}{Entire View of Topics per Month for MaxDB 7.500}

%\newslide

%\igninetycap{histogram-cropped}{}

%\newslide

\igHeigthyfivecap{histogram-cropped-scaled}{Top part of trend histogram, ordered by topic occurance}

@@

\igonecap{class-smear-plot-crop-scaled}{Trend Time Line: Trends plotted over time of MaxDB 7.500}

%\igbigcapb{class-smear-plot-crop-scaled-zoomed}{Zoomed in view of the repeating topics plotted}
\begin{specquoteh}
\begin{center}
\includegraphics[width=1.25\textwidth]{class-smear-plot-crop-scaled-zoomed} \\
Zoomed in view of the trend time line
\end{center}
\end{specquoteh}

%\igbigcapb{class-smear-plot-crop-scaled-zoomed}{Zoomed in view of the repeating topics plotted}

=Observations
* Topics could be named
** Certain words indicate a focus on
*** Maintenance
*** Bug Fixing
*** Portability
*** Potential 'ilities

=Observations
* Powerlaw distribution of repeating topic counts
** Most occured once
** A few were repeated 
*** less than 10\% of topics reoccur

=Unfinished
* Total Topics versus Monthly Topics
* Clean up plots

=Future work
* Cluster Naming
* Associate trends with software taxonomies
** Extension, associate Trends or Topics with purpoes by using wordnet and Taxonomies of software quality as suggested by Ernst et al.
* Validation

=Conclusions
* Contributions
** Auto extract trends
*** Present trends
** Apply topic analysis on timewindows rather than the entire project
